RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-03 doc/paper.tex
Start with round of revision in the Exp. section

Our \textsc{Rils}--\textsc{Rols} algorithm is implemented in Python version 3.x. All experiments are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode. The maximum computation time allowed for each run was set to 1h minutes, i.e., 3600 seconds.

The following 15 algorithms are compared: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp} and our \textsc{Rils}-\textsc{Rols} algorithm.

@@

SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and the environment for analysis, see~\cite{la2021contemporary}. It brought researchers an easy handled environment to evaluation, compare, and analyze their methods. Among all benchmark sets, we involve two real-world inspired benchmark sets, the ground-truth regression problems, into our computational evaluation: 
\begin{itemize}
	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that correspond to various natural laws.  
	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.

@@

	\item \textsc{Strogatz} benchmark set from~\cite{la2016inference}. 
	Each dataset is represented by a 2-state system of first-order, ordinary differential equations. 
	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  the current two states on which it depends. These equations describes various non-linear dynamics also exhibiting chaos.  The equations for some of the datasets that belong to this benchmark are shown in Table~\ref{table:strogatz-ODEs}.

@@

\end{itemize}
The above-mentioned benchmark sets may be biased as models which describe physical laws usually have  symmetries, periodicity w.r.t. some variables, internal separability on some variables etc. In that way, the search process and the search space can be biased and in-advance significantly reduced. Thus, some methods may get significant help with this regards, while some others may be in the subordinate situation. 
  In order to permit any kind of favoritism, we generate a set of randomly generated instances, called \textsc{Random}. These instances are generated according the following procedure. \fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}

All (15) competitor algorithms were run once per each instance.

>>>>

Our \textsc{Rils}--\textsc{Rols} algorithm is implemented in Python version 3.x. The experiments concerning our method are performed on a machine xx with xx GHz and a memory limit of xx GB in single-threaded mode.  
 The following 14 algorithms are compared to our approach: \textsc{AI-Feynman}, \textsc{GOMEA}, \textsc{Afp-Fe}, \textsc{Itea}, \textsc{Afp}, \textsc{Dsr}, \textsc{Operon}, the \textsc{Gplearn} from python package \textsc{gplearn}~\cite{stephens2016genetic}, \textsc{Sbp-Gp}, \textsc{Eplex}, \textsc{Bsr}, \textsc{Feat}, \textsc{Ffx}, \textsc{Mrgp}.

For the (14) competitors, the results are exported from \url{https://cavalab.org/srbench/results/}, also reported in~\cite{la2021contemporary}. 
The maximum computation time allowed for each run of \textsc{Rils}-\textsc{Rols} is set to 1h, i.e., 3600 seconds; note that the same runtime limit was used for all (14) competitors, see~\cite{la2021contemporary}.

All (15) competitor algorithms were run ten times per each instance.

@@

SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}. It brought researchers an easy handled environment to evaluation, comparisons, and analysis of their methods. Among all benchmark sets, we involve two real-world inspired benchmark sets, the ground-truth regression problems, into our computational evaluation: 
\begin{itemize}
	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that correspond to various natural laws.  
	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.  Among them, 115 regression problem instances are chosen in the experimental evaluation, with accordance to~\cite{la2021contemporary}.

@@

	\item \textsc{Strogatz} benchmark set from~\cite{la2016inference}. 
	Each dataset is represented by a 2-state system of first-order, ordinary differential equations. 
	The aim of each problem is to predict rate of change of the subsequent state w.r.t\  the current two states on which it depends. These equations describes natural processes described by non-linear dynamics  exhibiting chaos.  The equations for some of the datasets that belong to this benchmark are shown in Table~\ref{table:strogatz-ODEs}. These problem instances are downloadable from \url{https://github.com/lacava/ode-strogatz}. In overall, 14 ground-truth models are used to generate the problem instances used in the comparison, see~\cite{la2021contemporary}.

@@

\end{itemize}
The above-mentioned benchmark sets may be biased as models which describe physical laws that usually impose   symmetries, periodicity w.r.t. some variables, internal separability on some variables etc. In that way, the search process and the search space can be, in-advance, significantly reduced. Thus, some methods may get significant benefit with this regard, while some others may be in the subordinate situation. 
  In order to permit any kind of favoritism in the input data, we generate a set of randomly generated (non-biased) instances, labelled by \textsc{Random}. These instances are generated according the following procedure. \fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}
